\section*{Acknowledgement}

First and foremost, I am sincerely grateful to faculty members in Murai and Tokuda Laboratory, Professor Hideyuki Tokuda, Professor Jun Murai, Associate Professor Hiroyuki Kusumoto, Professor Osamu Nakamura, Associate Professor Kazunori Takashio, Assistant Professor Rodney D. Van Meter III, Associate Professor Keisuke Uehara, Associate Professor Jin Mitsugi, Lecturer Jin Nakazawa.

I would be extremely thankful to Professor Keiji Takeda for his endless help and valuable comments to my thesis. Without his help, I cannot even think of writing this thesis.

I give my special thank to Doctor Masayoshi Mizutani for his sincerely help and many advices since the time I first came to the lab.

I would like to thank to Mr.Kunihiko Shigematsu, Mr.Yuki Uehara, my friend Toshinori Usui, for listening	and giving me many useful discussion points. Their gentleness and encouragement helped me overcome hard periods in this one year. 
 
I would like to thank my friend Takuya Shibuta and Nguyen Tien Thanh, for their shape comments for the thesis structure and my English writing.

I would also like to thank all ISC group members, Mr.Toshinori Usui, Mr.Naoto Somi, Mr.Sekine Fuyuki, Mr.Vu Xuan Duong, Mr.Tomonori Yamamoto, Mr.Hiroki Yoshihara, Mr.Daido Yoshihara, Mr.Takao Oya, Mr.Reimon Arima, Mr.Hiroaki Kono, Mr.Takuya Yui, Mr.Makoto Komatsu, Mr.Do Trung Kien, Mr.Nguyen Anh Tien, Ms.Asuka Nakajima, Ms.Akane Mitsuki, Mr.Kouki Nakayasu, Mr.Kohei Tsuyuki, Mr.Yu Yoshida, Mr.Akifumi Fukaya, Ms.Urara Ozawa, who have given me numerous support and always cheer me up in my hard time. 

I owe my deep gratitude to members in Murai and Tokuda Laboratory who have been so friendly and kindly supporting me with my research.

Lastly and most importantly, I am heartily thankful to my family, including my grandparents, my parents, my older sister, and my older brother. Especially Ms.Nghiem Thi Hang for her greatest support in order to finish this thesis.
